What is the Effect of X on Y?

### 2023-08-29 latex-slides/slides.tex
Update slides
Update slide template

\documentclass[aspectratio=43]{beamer}
% \documentclass[aspectratio=169]{beamer}

@@

\input{preamble.tex}

@@

\begin{frame}{Components}{Blocks}
    \begin{block}{Regression Specification}
        The main specificaiton is as follows:

        \[
            y_{it} = X_{it} \beta + \mu_i + \varepsilon_{it}
        \]
    \end{block}
\end{frame}

@@

@@

  \cranberry{Test sentence with \textbackslash color\{cranbery\}}

  \slate{Test sentence with \textbackslash color\{slate\}}

  \jet{Test sentence with \textbackslash color\{jet\}}

  \asher{Test sentence with \textbackslash color\{asher\}}
\end{frame}

\begin{frame}{Components}{Colored Boxes}
  \bgNavy{Test word} with \textbackslash bgNavy\{...\}

@@

@@

\begin{frame}{Components}{Two Columns with Figure}
    \begin{columns}[T]
    \vspace{0pt}
    \begin{column}{.60\textwidth}
        \includegraphics[width=\textwidth]{img/kanagawa.jpg}

    \begin{column}{.40\textwidth}
        \begin{itemize}
            \item A point about the figure that is potentially important.
            \item Another point about the figure that is also potentially important.
        \end{itemize}
    \end{column}
    \end{columns}
\end{frame}

@@

\begin{frame}

% Adjust Font Size to make table fit   
\begin{table}[!htbp]
    \caption{Regression Results} 
    \label{}

    \begin{adjustbox}{max width = \textwidth, width = 0.5\textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} l *{2}{r} @{}} 
                \toprule
                & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
                \cline{2-3} \\
                & (1) & (2)\\ 
                \midrule

                \only<1>{
                    Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
                    &  (0.149) & (0.129) \\
                }
                \only<2>{
                    \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
                    &  (0.149) & (0.129) \markbottomright{ex1} \\
                }
                No Special Privileges & -0.104 & $-$0.103  \\ 
                & (0.135) & (0.129) \\
                Opportunity to Learn & 0.249 & 0.238$^{*}$ \\ 
                & (0.160) & (0.139) \\
                Performance-Based Raises & -0.033 &  \\ 
                & (0.202) & \\
                Too Critical & 0.015 &  \\ 
                & (0.147) & \\
                Advancement & 11.011 & 11.258 \\ 
                & (11.704) & (7.318) \\

@@

{\small
Use \textbackslash marktopleft\{name\} and \textbackslash markbottomright\{name\} to create box.
}
\end{frame}

@@

% 4:3 ratio for figures
% or else it will have white space
\imageframe{img/kanagawa.jpg}

\begin{frame}{Figure}{Full-size Figures}
    You can use the command \textbackslash imageframe\{img-path\} and it will create a full-frame of a picture.

    \begin{itemize}
        \item Ideally, your figure is the same aspect as the frame $4:3$ or $16:9$ or else there will be white space in one of the directions.
    \end{itemize}
\end{frame}

\begin{frame}{Figure}{}
    \begin{center}
        \resizebox{0.9\columnwidth}{!}{%
            \includegraphics{img/kanagawa.jpg}
        }
    \end{center}
\end{frame}

@@

\begin{frame}{Appendix Slide}\label{appendix1}

\begin{table}
    \caption{Summary Statistics}
    \label{appendix_summ_stat}
    \begin{adjustbox}{max width = \textwidth, width = 0.8 \textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} lccccccc @{}} 
                \toprule
                Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
                \hline \\[-1.8ex] 
                rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
                complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
                privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
                learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
                raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
                critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
                advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
                \bottomrule
            \end{tabular} 
            % Notes 
            \begin{tablenotes}
                \item \textit{Notes.} Using R base dataframe attitude.
            \end{tablenotes}
        \end{threeparttable}
    \end{adjustbox}
\end{table}

>>>>

\documentclass[aspectratio=169]{beamer}
% \documentclass[aspectratio=43]{beamer}

% Define `accent`/`accent2` colors for theme customization
\definecolor{accent}{HTML}{006896}
\definecolor{accent2}{HTML}{E64173}

% Beamer theme
\input{preamble.tex}

@@

@@

\begin{frame}{Components}{Blocks}
  \begin{block}{}
    The main specificaiton is as follows: 
    $$
      y_{it} = X_{it} \beta + \mu_i + \varepsilon_{it}
    $$
    With $\mu_i$ being unit fixed effects.
  \end{block}
\end{frame}

\begin{frame}{Components}{Blocks}
  \begin{purpleBlock}{}
      This is a purple block
  \end{purpleBlock}

  \begin{cranberryBlock}{With Title}
    This is a cranberry block
  \end{cranberryBlock}
\end{frame}

@@

  \teal{Test sentence with \textbackslash teal\{...\}}

@@

  \cranberry{Test sentence with \textbackslash color\{cranbery\}}
\end{frame}

\begin{frame}[plain]
  \bgNavy{Test word} with \textbackslash bgNavy\{...\}

@@

  \vspace{2.5mm}
  \bgOrange{Test word} with \textbackslash bgOrange\{...\}

  \vspace{2.5mm}
  \bgTeal{Test word} with \textbackslash bgTeal\{...\}

@@

\begin{frame}{Components}{Two Columns with Figure}
    \begin{columns}[T]
    \vspace{0pt}
    \begin{column}{.6\textwidth}
        \includegraphics[width=0.9\textwidth]{img/kanagawa.jpg}

        \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
    \end{column}
    \hfill
    \begin{column}{.4\textwidth}
        \begin{itemize}
            \item A point about the figure that is potentially important.
            \item Another point about the figure that is also potentially important.
        \end{itemize}
    \end{column}
    \end{columns}
\end{frame}

@@

\begin{frame}{Table}

\begin{columns}[T]
  \vspace{0pt}
  \begin{column}{.6\textwidth}
    % Adjust Font Size to make table fit   
    \begin{table}[!htbp]
      % \caption{Regression Results} 
      \label{}

      \begin{adjustbox}{max width = \textwidth, width = 0.8 \textwidth, center}
          \begin{threeparttable}
              \begin{tabular}{@{} l *{2}{r} @{}} 
                  \toprule
                  & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
                  \cline{2-3} \\
                  & (1) & (2)\\ 
                  \midrule

                  \only<1>{
                      Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
                      &  (0.149) & (0.129) \\
                  }
                  \only<2>{
                      \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
                      &  (0.149) & (0.129) \markbottomright{ex1} \\
                  }
                  No Special Privileges & -0.104 & $-$0.103  \\ 
                  & (0.135) & (0.129) \\
                  Opportunity to Learn & 0.249 & 0.238$^{*}$ \\ 
                  & (0.160) & (0.139) \\

@@

      \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
  \end{column}
  \hfill
  \begin{column}{.4\textwidth}
      \begin{itemize}
          \item Use \texttt{\textbackslash marktopleft\{name\}} and \texttt{\textbackslash markbottomright\{name\}} within the table to create box.
          \item Using \texttt{\textbackslash only} or \texttt{\textbackslash on} lets you conditionally display box
      \end{itemize}
  \end{column}
\end{columns}

\end{frame}

@@

% 4:3 ratio for figures
% or else it will have white space
\imageframe{img/kanagawa_16_9.png}

\begin{frame}{Figure}{Full-size Figures}
  You can use the command \texttt{\textbackslash imageframe\{img-path\}} and it will create a full-frame of a picture.

  \begin{itemize}
    \item Ideally, your figure is the same aspect as the frame \texttt{4:3} or \texttt{16:9} or else there will be white space in one of the directions.
  \end{itemize}
\end{frame}

\begin{frame}{Figure}{}
    \begin{center}
        \resizebox{0.85\columnwidth}{!}{%
            \includegraphics{img/kanagawa_16_9.png}
        }
    \end{center}
\end{frame}

@@

\begin{frame}{Appendix Slide}\label{appendix1}
\begin{table}
    \caption{Summary Statistics}
    \label{appendix_summ_stat}
    \begin{adjustbox}{max width = \textwidth, width = 0.7\textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} lccccccc @{}} 
                \toprule
                Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
                \hline \\[-1.8ex] 
                rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
                complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
                privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
                learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
                raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
                critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
                advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
                \bottomrule
            \end{tabular} 
            % Notes 
            \begin{tablenotes}
                \item \textit{Notes.} Using R base dataframe attitude.
            \end{tablenotes}
        \end{threeparttable}
    \end{adjustbox}
\end{table}
